--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Literature

Here is a review of existing methods.

<!--chapter:end:02-literature.Rmd-->

# Methods

We describe our methods in this chapter.

<!--chapter:end:03-method.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Histological Protocols
## Alizarin Staining

### PURPOSE: Alizarin staining of fixed adult stickleback.

### MATERIALS:

- 0.5% Alizarin red S Stock: To make 50 mls add 0.25g alizarin red S powder to 50 ml water.
- 0.025% Alizarin Stain: To make 100 mls: Add 500µl 0.5% alizarin red S (stock) to 99.5ml 1% KOH
- 1 Liter: Add 5ml 0.5% alizarin red S (stock) to 9950ml (1 liter) 1%KOH

3% H202/0.5%KOH: {#h2020.5koh .subhead2}

Mix and keep at 4C; Before using, bring to room temperature to hold down
introducing bubbles under the skin: 0.5ml 6%H202 & 0.5ml 1%KOH.

MESAB: {#mesab .subhead2}

Tricaine: 3-amino benzoic acid ethyl ester from Sigma (Cat \# A-5040).
Mix in fish safe container with a stir bar:

-   400 mg tricaine powder
-   800 mg Na2HPO4 (anhydrous)
-   100 ml glass distilled water

Adjust to \~pH 7 with a drop at a time of 1N NaOH or 1N HCl if needed
but it's usually right if you weigh the sodium phosphate carefully and
measure the water with a graduated cylinder.

For storage: Aliquot into 6 x 25 ml fish safe plastic bottles and store
at 4C. Label with date made and use within a couple of weeks.

8% PFA: {#pfa .subhead2}

-   8 g Pelleted PFA (Ted Pella, Inc.; cat\# 18501)
-   90 ml dH2O
-   25 drops 1N NaOH

1.  Heat at very low heat and stir until solution clears.
2.  Add 25 drops 1N HCl. pH should be 7.0-7.2.
3.  Filter and store at 4C not more than 1 week.
4.  Use as 4% PFA: dilute 1:1 with 2X PBS, do not store solution more
    than a few hours.

2X PBS {#x-pbs .subhead2}

-   1.6% NaCl
-   0.04% KCl
-   0.04 M PO4 pH 7.0- 7.3


### Procedure:


Day

Step

Time for Step

Date and Time

1

2h-8h at R/T depending on size on shaker.

1h or longer at R/T on shaker.

Without agitation and with lid open until eyes start to lighten and all
skin pigment is gone (usually about an hour or more)


2

2 h to O/N at R/T on shaker


2 h to overnight O/N at R/T on shaker.\
Check for bone staining.


R/T on shaker until excess stain in tissue is gone.


Without agitation

Wild caught specimens are put in 100% EtOH in the field and then
rehydrated and put into 4% when back in the lab.

<!--chapter:end:05-protocols.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->

